### 2004-07-12 Documentation/Paper/paper.tex
*** empty log message ***

\bi
 \item 
  \figu{GLOBES} and main features
 \item
  Physics basics: For what purpose? What are difficulties
 \item
  Detector simulation: What happens there?
 \item
  References for work done with \GLOBES\
 \item
  Parts of \GLOBES\
 \item 
  \figu{GLOBES} and main features
\ei

@@

Minimizers?

>>>>

\bi
 \item 
  \figu{GLOBES} and main features
 \item
  Physics basics: For what purpose? What are difficulties
 \item
  Detector simulation: What happens there?
 \item
  References for work done with \GLOBES\
 \item
  Parts of \GLOBES\
 \item 
  \figu{GLOBES} and main features:
  \bi
   \item
    3-flavor analysis
   \item
    Matter density profile+uncertainty
   \item
    Full detector simulation
   \item
    Up to 32 experiments simultaneously
   \item
    Full n-parameter correlation
   \item
    Localization of degeneracies
  \ei
\ei

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=16cm]{projex}
\end{center}
\mycaption{\label{fig:projex} Left plot: Example for a  correlation between $\stheta$ and $\deltacp$ (for 1 d.o.f. only). Right plot: The $\chi^2$-value of the projection onto the $\stheta$-axis as function of $\stheta$. The projection onto the  $\stheta$-axis is obtained by finding the minimum $\chi^2$-value for each fixed value of $\stheta$ in the left-hand plot, \ie, along the gray vertical lines. The thick gray curve marks the position of these minima in the left-hand plot. The arrows mark the obtained fit ranges for $\stheta$ at the $3 \sigma$ confidence level (1 d.o.f.), \ie , the precision of $\stheta$.}
\end{figure}

In order to use \GLOBES , a C~library is linked with the application
software. This library provides the user's interface functions.
It allows to load \AEDL\ files, initialize the experiments, and
have access to various $\Delta \chi^2$-functions including any combination
of systematics and correlations. In addition, it provides low-level
access to oscillation probabilities and event rates, and allows
the readout and modification of many experiment parameters at running time.

The most sophisticated feature of the user's interface is the
possibility to include the full multi-parameter correlation among
all oscillation parameters. Together with the matter densities
of the $N$ loaded experiments ($N \ge 1$), the neutrino oscillation parameter space in \GLOBES\ has $6+N$ dimensions. In the $\chi^2$-approach,
the allowed region of $k$ ($1\le k<6+N$) fit parameters (at the chosen confidence level) is obtained as the projection of the $6+N$-dimensional fit manifold onto the $k$-dimensional hyperplane. For example,
for the precision of the parameter $\stheta$ only, the fit manifold
needs to be projected onto the $\stheta$-axis. One can easily imagine
that the computation of the full multi-parameter correlation is
very expensive with a grid-based method. However, the topology
of the neutrino oscillation parameter space is well investigated and
rather fortunate. Therefore, we use local minimization for each
solution in the parameter space at the chosen confidence level,
where tools for the location of (disconnected) degenerate solutions 
are provided. For this process, the $6+N$-dimensional local minimizer
is started at the ``guessed'' solution (such as from analytical 
knowledge) and runs into the local minimum. In \figu{projex},
this minimization is illustrated at the simple example of a 
two-parameter correlation at a neutrino factory.

As we have discussed in the last section, the matter density of
each experiment is treated as an addition parameter, which is known
from external measurement with a certain precision. In principle, 
the \GLOBES\ user's interface allows such externally imposed
precisions for all oscillation parameters. This feature turns out
to be especially useful for input from the solar neutrino experiments,
since they provide better precisions for the solar neutrino
osillation parameters $\sdm$ and $\theta_{13}$ than the long-baseline
 experiments themselves.
